Data Story

### 2023-10-19 index.qmd
Update
Update index.qmd
Project Update

![](images/namelogo.png)

# [Link to Course Content from Week 1 to Week 9](https://github.com/mrzknrns/mrzknrns.git){.uri}

@@

img1 <- readPNG("src/images//me_icon.png")
img2 <- readPNG("src/images/68FD47AF-F084-4FCC-85AC-4712EEC1B685.PNG")

>>>>

![](src/images/namelogo.png)

### [Link to Course Content from Week 1 to Week 9](https://github.com/mrzknrns/mrzknrns.git){.uri}

@@

img1 <- readPNG("src/images/me_icon.png")
img2 <- readPNG("src/images/68FD47AF-F084-4FCC-85AC-4712EEC1B685.PNG")
